A studyforrest extension, an annotation of spoken language in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-05-25 paper/main.tex
updated text of to dos (instead of just deleting them)

% intro to analysis
We implemented a standard three-level, voxel-wise general linear model (GLM) to
average parameter estimates across the eight stimulus segments, and later across
19 subjects.
% 1st lvl
At the first level analyzing each segment for each subject individually, we
created 26 regressors based on events drawn from the annotation (see Table
\ref{tab:regressors}).
% part-of-speech labels: labels to events, top 20
The 20 most often occurring detailed part-of-speech labels (\texttt{nn} with
N=\rNnAll\space to text{prf} with N=\rPrfAll) were modeled as boxcar function
from onset to offset of each word \todo{This has errors that I do not know how
to fix; sorry, unclear what you mean by that}.
% path-of-speech labels: remaining labels
The remaining other part-of-speech labels were pooled to a single new label
(\texttt{tag\_other}; N=\rTagotherAll) and each event was modeled as a boxcar
function from onset to offset of the corresponding word\todo{I do not know what
this means; hope it got clearer now}.
% phonemes
The top 80 phonemes (\texttt{n} with N=6053 to \texttt{IY1} with N=32) were
pooled to \texttt{phonemes} (N=\rPhonesAll) and each event modeled as boxcar
function from onset to offset of the corresponding phoneme.\todo{Does that mean
they share events with "other"}.
% sentence (endings)
The end of each complete grammatical sentence was modeled as an impulse event
(N=\rSentenceAll) to capture variance of sentence comprehension\todo{Why? Above
it says 'we tested if similar linguistic concepts providing high semantic
information (proper nouns and nouns)'. What does this need sentences for?}.
% no-speech intro
``No-speech'' events (\texttt{no-sp}; N=\rNospAll) serving as a control
condition were created by the following rationale: events were fitted into
longer lasting intervals between onsets and offsets of words and thus within
intervals without audible speech \todo{Why assumed? Isn't the point of the
annotation to "know"? => Words where chosen to carefully; intervals don't
contain any audible speech with 98 perc. certainty}
% minimum distance to words
Each event of the no-speech condition had to have a minimum distance of
\unit[1.8]{s} to an onsets or offsets of a word, and to each onset to another
event of the no-speech condition.
% length of no-speech events
A length of \unit[70]{ms} was chosen for no-speech events matching the average
length of phonemes.
% low-level nuisance regressors
Lastly, we used events\todo{They are not really events, but a continuous
nuisance regressor; okay, how do you phrase that correctly?} reflecting
low-level auditory features (left-right difference in volume and root mean
squared volume) averaged across the length of every movie frame (\unit[40]{ms}).
All events were convolved with FSL's ``Double-Gamma HRF'' as a model of the
hemodynamic response function to create the actual regressors.
% reference to figure ``correlation of regressors''
The Pearson correlation coefficients of the 26 regressors across the time course
of all stimulus segments can be seen in Figure \ref{fig:reg-corr}.
% temporal derivatives
Temporal derivatives were also included in the design matrix and the design was
subjected to the same temporal filtering as the BOLD time series.
% motion parameters
Finally, six motion parameters were used as additional nuisance regressors.

@@

\todo{“partial brain coverage” / FoV. MIH: Could become an issue. In the data paper we showed the coverage. Maybe just ref the figure => gonna take a look how I can adjust the script to get a FoV mask from the data and use it during plotting; otherwise: ref to paper}
\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figures/slicescolorbars}
  \caption{Mixed-effects group-level (N=14) GLM contrasts for the audio-description of the movie Forrest Gump. All cluster (Z>3.4, p<0.05 cluster-corrected; MNI template space)}.
\label{fig:results}
\end{figure*}

@@

\todo[inline]{Lass uns bzgl. der Discussion am besten unterhalten; im Grunde
geht es darum, wie weit ich ins Detail gehen soll (kann nämlich viel zu sehr ins
Detail gehen); im Grunde geht es imo nicht darum, alle Cluster inkl. Areale
durchzudiskutieren, sondern zu kommunizieren, dass die Anno brauchbar ist; wie
dem auch sei: Hier wird noch Inhalt nach dem Lesen der Reviews hinzukommen}
% words > no-speech
In the contrast words > no-speech, we find increased hemodynamic activity in a
bilateral cortical network including temporal, parietal and frontal regions
related to processing spoken language \citep{friederici2011brain,
hickok2007cortical,price2012twentyyears}.
% similarities to previous naturalistic speech paradigms
Our results are similar to results of studies that implemented an ISC approach
to analyze fMRI data of naturalistic auditory stimuli \citep{honey2012not,
lerner2011topographic, silbert2014coupled}.
% dissimilarities
Contrary to previous studies, we do not find increased medial activation in the
precuneus or medial frontal cortex. This could be attributed to the fact that
our contrast does not \todo{Which contrast captures ANY social aspects? => the
COPEs in the references} capture social aspects of the narrative
\citep{ferstl2008extended, mar2011neural}\todo{check it}.
% (proper) nouns > con
The two contrasts contrasting nouns and proper nouns respectively to coordinate
junctions lead to unexpected results\todo{That seems like an unfortunate
statement. We make this analysis to show expected results to conclude that the
annotation is good. But we get unexpected results and conclude; the contrast is
shit; cf. following explanation}.
% cluster location
Increased activation is partially located in early sensory regions (Heschl's
Gyrus; \citep{saenz2014tonotopic}) and most prominently adjacent regions
bilaterally (planum temporale; superior temporal gyrus;
\citep{arsenault2015distributed, mesgarani2014phonetic}).
% interpretation 1a: large amount of semantically different nouns > narrow
% concept (conjunctions)
This could be attributed to the fact that a high count of heterogeneous nouns
(N=\rNnAll) and proper nouns (N=\rNeAll) were averaged across all 300 semantic
dimensions (cf. \citep{mitchell2008predicting, huth2016natural}), and contrasted
to coordinate conjunctions that offered a comparably small amount of events
(N=\rKonAll).
% interpretation 1b: not just narrow concept but also dominated by just two
% different words
Moreover, the coordinate junctions (\texttt{kon}) mostly comprises event of the
words ``and'' (N=392) and ``but'' (N=49) and thus offered only a small amount of
variance.
% interpretation 2
A second explanation might be that our phoneme regressors that assumed linear
summation of approximately 70 ms lasting events in quick succession did not
capture a sufficiently amount of nuisance variance\todo{Reviewer 2 will ask: If
you knew all these issues, why did you do it then? hindsight bias after
exploratory analyses?!}.
% but...
Nevertheless and more importantly to access the validity of the dataset is the
fact that two similar linguistic concepts (nouns and proper nouns) embedded in a
naturalistic stimulus that was not designed for linguistic research lead to
similar activation patterns\todo{That statement is only true, if both contrasts
are not (solely) driven by the conjunctions. There is no evidence in the paper
that this is not the case.}
% Within the language processing systems, early sensory regions are specialized
% for representing the immediate physical properties of the environment (form),
% while higher order regions extract increasingly abstract content (Davis and
% Johnsrude, 2003; Quiroga et al., 2005; Okada et al., 2010).

@@

\section*{Conclusions}
\todo[inline]{the paper needs to serve a purpose.
One is, of course, to be documentation for the annotation.
Another is to attract people to use this work for their own studies.
I would even argue that this is the \textit{main} purpose, given that the annotation in itself represents to scientific progress.
The need to give an accurate assessment what this can be used for and what is problematic or impossible.
ATM this is the only statement in this regard:
'facilitates modeling of hemodynamic brain responses correlating with speech-related events' and the only indication of purpose is 'additional confound measures'.
I think this is incongruent with the amount of work and the level of detail of
this annotation; öööööhh, okay. Mir sind da jetzt über 2 Tage wenig Superlative eingefallen, die über den bisherigen Text hinausgehen; fehlt mir wohl die geeignete Perspektive}
% state what you think are the main conclusions that can be realistically drawn from the findings in the paper, taking care not to make claims that cannot be supported.
As an extension of the studoforrest dataset, we present an annotation of spoken language in the two hours lasting ``research cut'' of the audio-visual movie ``Forrest Gump'' and its temporally aligned audio-description.
We annotated the onset and offset of sentences, words and phonemes, and the corresponding speaker's identity.
An additional tagging of each word's linguistic features and the public nature of the dataset enable independent working groups to create sophisticated models of hemodynamic activity correlating with speech-related events in a naturalistic stimulus.
Results of our dataset validating analysis that we run as a proof of concept show that the annotation's content can indeed / in principle be used to isolate/track speech-related networks in the human brain under life-like conditions.

@@

\subsection*{Grant information}

COH was supported by a graduate stipend from the German federal state of
Saxony-Anhalt and MH was supported by funds from the German federal state of
Saxony-Anhalt and the European Regional Development Fund (ERDF), Project:
Center for Behavioral Brain Sciences (CBBS). Work on the adapting data
management technology for this study was in part supported by the European
Union's Horizon 2020 Research and Innovation Programme under Grant Agreement
no. 785907 (HBP SGA2).

\subsection*{Acknowledgements}
We are grateful to \href{www.florianschurz.de}{Florian Schurz} who initiated doing the annotation of the descriptive nouns\todo{should it still be here? or move in PPA paper?}, and performed the preliminary annotation of nouns. Christian O. Häusler is also grateful to Valeri Kippes who took care of the author's mental sanity by providing excellent training at his gym in Jülich during the mentally draining period of manual corrections of the annotation.

>>>>

% intro to analysis
We implemented a standard three-level, voxel-wise general linear model (GLM) to
average parameter estimates across the eight stimulus segments, and later across
19 subjects.
% 1st lvl
At the first level analyzing each segment for each subject individually, we
created 26 regressors based on events drawn from the annotation (see Table
\ref{tab:regressors}).
% part-of-speech labels: labels to events, top 20
The 20 most often occurring detailed part-of-speech labels (\texttt{nn} with
N=\rNnAll\space to text{prf} with N=\rPrfAll) were modeled as boxcar function
from onset to offset of each word \todo{This has errors that I do not know how
to fix; sorry, unclear what you mean by that}.
% path-of-speech labels: remaining labels
The remaining other part-of-speech labels were pooled to a single new label
(\texttt{tag\_other}; N=\rTagotherAll) and each event was modeled as a boxcar
function from onset to offset of the corresponding word\todo{I do not know what
this mean; CH: hope it got clearer now}.
% phonemes
The top 80 phonemes (\texttt{n} with N=6053 to \texttt{IY1} with N=32) were
pooled to \texttt{phonemes} (N=\rPhonesAll) and each event modeled as boxcar
function from onset to offset of the corresponding phoneme.\todo{Does that mean
they share events with "other"; CH: dunno what you mean, but text should be
clearer now}.
% sentence (endings)
The end of each complete grammatical sentence was modeled as an impulse event
(N=\rSentenceAll) to capture variance of sentence comprehension\todo{Why? Above
it says 'we tested if similar linguistic concepts providing high semantic
information (proper nouns and nouns)'. What does this need sentences for? CH:
it is kinda nuisance regressor}.
% no-speech intro
``No-speech'' events (\texttt{no-sp}; N=\rNospAll) serving as a control
condition were created by the following rationale: events were fitted into
longer lasting intervals between onsets and offsets of words and thus within
intervals without audible speech \todo{Why assumed? Isn't the point of the
annotation to "know"? CH: words where chosen to carefully; intervals don't
contain any audible speech with >98 perc. certainty}
% minimum distance to words
Each event of the no-speech condition had to have a minimum distance of
\unit[1.8]{s} to an onsets or offsets of a word, and to each onset to another
event of the no-speech condition.
% length of no-speech events
A length of \unit[70]{ms} was chosen for no-speech events matching the average
length of phonemes.
% low-level nuisance regressors
Lastly, we used events\todo{They are not really events, but a continuous
nuisance regressor; CH: okay, how do you phrase that correctly?} reflecting
low-level auditory features (left-right difference in volume and root mean
squared volume) averaged across the length of every movie frame (\unit[40]{ms}).
All events were convolved with FSL's ``Double-Gamma HRF'' as a model of the
hemodynamic response function to create the actual regressors.
% reference to figure ``correlation of regressors''
The Pearson correlation coefficients of the 26 regressors across the time course
of all stimulus segments can be seen in Figure \ref{fig:reg-corr}.
% temporal derivatives
Temporal derivatives were also included in the design matrix and the design was
subjected to the same temporal filtering as the BOLD time series.
% motion parameters
Finally, six motion parameters were used as additional nuisance regressors.

@@

\todo{“partial brain coverage” / FoV. MIH: Could become an issue. In the data
paper we showed the coverage. Maybe just ref the figure. CH: gonna take a look how I can adjust the script to get a FoV mask from the data and use it during plotting; otherwise: ref to paper}
\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figures/slicescolorbars}
  \caption{Mixed-effects group-level (N=14) GLM contrasts for the audio-description of the movie Forrest Gump. All cluster (Z>3.4, p<0.05 cluster-corrected; MNI template space)}.
\label{fig:results}
\end{figure*}

@@

\todo[inline]{Lass uns bzgl. der Discussion am besten unterhalten; im Grunde
geht es darum, wie weit ich ins Detail gehen soll (kann nämlich viel zu sehr ins
Detail gehen); im Grunde geht es imo nicht darum, alle Cluster inkl. Areale
durchzudiskutieren, sondern zu kommunizieren, dass die Anno brauchbar ist; wie
dem auch sei: Hier wird noch Inhalt nach dem Lesen der Reviews hinzukommen}
% words > no-speech
In the contrast words > no-speech, we find increased hemodynamic activity in a
bilateral cortical network including temporal, parietal and frontal regions
related to processing spoken language \citep{friederici2011brain,
hickok2007cortical,price2012twentyyears}.
% similarities to previous naturalistic speech paradigms
Our results are similar to results of studies that implemented an ISC approach
to analyze fMRI data of naturalistic auditory stimuli \citep{honey2012not,
lerner2011topographic, silbert2014coupled}.
% dissimilarities
Contrary to previous studies, we do not find increased medial activation in the
precuneus or medial frontal cortex. This could be attributed to the fact that
our contrast does not \todo{Which contrast captures ANY social aspects? CH: the
COPEs in the references} capture social aspects of the narrative
\citep{ferstl2008extended, mar2011neural}\todo{check it}.
% (proper) nouns > con
The two contrasts contrasting nouns and proper nouns respectively to coordinate
junctions lead to unexpected results\todo{That seems like an unfortunate
statement. We make this analysis to show expected results to conclude that the
annotation is good. But we get unexpected results and conclude; CH: the contrast
turned out to yield the result; cf. following explanation; I don't feel
comfortable of HARKing}.
% cluster location
Increased activation is partially located in early sensory regions (Heschl's
Gyrus; \citep{saenz2014tonotopic}) and most prominently adjacent regions
bilaterally (planum temporale; superior temporal gyrus;
\citep{arsenault2015distributed, mesgarani2014phonetic}).
% interpretation 1a: large amount of semantically different nouns > narrow
% concept (conjunctions)
This could be attributed to the fact that a high count of heterogeneous nouns
(N=\rNnAll) and proper nouns (N=\rNeAll) were averaged across all 300 semantic
dimensions (cf. \citep{mitchell2008predicting, huth2016natural}), and contrasted
to coordinate conjunctions that offered a comparably small amount of events
(N=\rKonAll).
% interpretation 1b: not just narrow concept but also dominated by just two
% different words
Moreover, the coordinate junctions (\texttt{kon}) mostly comprises event of the
words ``and'' (N=392) and ``but'' (N=49) and thus offered only a small amount of
variance.
% interpretation 2
A second explanation might be that our phoneme regressors that assumed linear
summation of approximately 70 ms lasting events in quick succession did not
capture a sufficiently amount of nuisance variance\todo{Reviewer 2 will ask: If
you knew all these issues, why did you do it then? hindsight bias/HARKing after
exploratory analyses?!}.
% but...
Nevertheless and more importantly to access the validity of the dataset is the
fact that two similar linguistic concepts (nouns and proper nouns) embedded in a
naturalistic stimulus that was not designed for linguistic research lead to
similar activation patterns\todo{That statement is only true, if both contrasts
are not (solely) driven by the conjunctions. There is no evidence in the paper
that this is not the case.}
% Within the language processing systems, early sensory regions are specialized
% for representing the immediate physical properties of the environment (form),
% while higher order regions extract increasingly abstract content (Davis and
% Johnsrude, 2003; Quiroga et al., 2005; Okada et al., 2010).

@@

\section*{Conclusions} \todo[inline]{the paper needs to serve a purpose.  One
is, of course, to be documentation for the annotation.  Another is to attract
people to use this work for their own studies.  I would even argue that this is
the \textit{main} purpose, given that the annotation in itself represents to
scientific progress.  The need to give an accurate assessment what this can be
used for and what is problematic or impossible.  ATM this is the only statement
in this regard: 'facilitates modeling of hemodynamic brain responses correlating
with speech-related events' and the only indication of purpose is 'additional
confound measures'.  I think this is incongruent with the amount of work and the
level of detail of this annotation; CH: let's discuss that personally}
% state what you think are the main conclusions that can be realistically drawn
% from the findings in the paper, taking care not to make claims that cannot be
% supported.  intro
As an extension of the studyforrest dataset, we present an annotation of spoken
language in the two hours lasting ``research cut'' of the audio-visual movie
``Forrest Gump'' and its temporally aligned audio-description.
% what we did
We annotated the onset and offset of sentences, words and phonemes, and the
corresponding speaker's identity.
% what for
An additional tagging of each word's linguistic features and the public nature
of the dataset enable independent working groups to create sophisticated models
of hemodynamic activity correlating with speech-related events in a naturalistic
stimulus.
% results
Results of our dataset validating analysis that we run as a proof of concept
show that the annotation's content can indeed / in principle be used to
isolate/track speech-related networks in the human brain under life-like
conditions.

@@

\subsection*{Grant information}
COH was supported by a graduate stipend from the German federal state of
Saxony-Anhalt and MH was supported by funds from the German federal state of
Saxony-Anhalt and the European Regional Development Fund (ERDF), Project:
Center for Behavioral Brain Sciences (CBBS). Work on the adapting data
management technology for this study was in part supported by the European
Union's Horizon 2020 Research and Innovation Programme under Grant Agreement
no. 785907 (HBP SGA2).

\subsection*{Acknowledgements}
COH is grateful to Valeri Kippes who took care of the author's mental sanity by providing excellent training at his gym in Jülich during the mentally draining period of manual corrections of the annotation.
